Milestone 4: Datasets Generation

### 2019-12-11 perf_release_criteria/milestone_4/ms_4_training_subsetting_calculation.Rmd
Updated notebook with release health placeholders.

```{r train, message=FALSE}
# fs1 <- c('TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT') 
# fs1 <- names(get_m2_metric_map()) # FIXME

model <- train_matchit(df_train_x, outcomes, add_interactions = TRUE, replace = FALSE, 
                         caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
```

@@

Calculate the Release Health Metrics

@@

```{r serialize_dataset}
image_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
image_file_path <- file.path('data', image_file_name)
save(df_train_f, df_predict_f, df_train_x, file = image_file_path)

gcs_file_path <- file.path('data', 'milestone4', image_file_name)
```

Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r gcs_file_path`.

```{r gcp_storage_push, warning=FALSE}
Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "~/certs/moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")

@@

upload_try <- gcs_upload(image_file_path, name = gcs_file_path)
upload_try
```

@@

Training and prerelease datasets
```{r big_query_write}
project <- "moz-fx-dev-cdowhyglund-subbeta"
# project <- "moz-fx-data-bq-data-science"

@@

@@

Release health Metrics
```{r bq_release_health_metrics}

>>>>

```{r train, message=FALSE, error=FALSE}
model <- train_matchit(df_train_x, outcomes, add_interactions = TRUE, replace = FALSE, 
                         caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
```

@@

Calculate the Release Health Metrics:
**TBD**

@@

```{r serialize_datasets}
# training datasets
train_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
train_file_path <- file.path('data', train_file_name)
save(df_train_f, df_predict_f, df_train_x, model, file = train_file_path)
gcs_train_file_path <- file.path('data', 'milestone4', train_file_name)

# final prelease subsetted dataset
prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
prerelease_file_path <- file.path('data', prerelease_file_name)
save(predictions, file = prerelease_file_path)
gcs_prerelease_file_path <- file.path('data', 'milestone4', prerelease_file_name)

# Release health metrics
release_health_file_name <- paste('df_release_health_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
release_health_file_path <- file.path('data', release_health_file_name)
# save(df_release_health_f, df_predict_f, df_release_health_x, file = release_health_file_path)
gcs_release_health_file_path <- file.path('data', 'milestone4', release_health_file_name)
```

Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, to the following files:

* `r gcs_train_file_path`
* `r gcs_prerelease_file_path`
* `r gcs_release_health_file_path`

```{r gcp_train_storage_push, warning=FALSE}
Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "~/certs/moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")

@@

upload_try <- gcs_upload(train_file_path, name = gcs_train_file_path)
upload_try
```

```{r gcp_prelease_storage_push, warning=FALSE}
upload_try <- gcs_upload(prerelease_file_path, name = gcs_prerelease_file_path)
upload_try
```

```{r gcp_health_metrics_storage_push, warning=FALSE}
# upload_try <- gcs_upload(gcs_release_health_file_path, name = gcs_file_path)
# upload_try
```

@@

Training and prerelease datasets
```{r big_query_write}
project <- "moz-fx-dev-cdowhyglund-subBeta"
# project <- "moz-fx-data-bq-data-science"

@@

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "training",
         table   = "ccd_subbeta_training_final") %>%
  bq_table_upload(values = df_train_x,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_train_x) )

@@

Release health Metrics
```{r bq_release_health_metrics}
# bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
#          dataset = "prerelease",
#          table   = "ccd_subbeta_prerelease_health_metrics") %>%
#   bq_table_upload(values = release_health_df,
#                   create_disposition = "CREATE_IF_NEEDED",
#                   write_disposition = "WRITE_APPEND",
#                   fields = as_bq_fields(release_health_df) )
```
